Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-07 volunteer-clouds-ieee-ci-si.tex
Adds duration graphs

We will have to analyze experiment data a bit further to find out why
this happens and also if there is some pattern in the three sets of
experiments. An interesting question to ask, for instance, is if
adding more computers makes the experiment take less.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=0.32\linewidth]{img/time-vs-ips-OS-4-4.png}
\includegraphics[width=0.32\linewidth]{img/time-vs-ips-OS-4-24.png}
\includegraphics[width=0.32\linewidth]{img/time-vs-ips-OS-7-31.png}
\caption{Duration of experiments vs. number of different IPs (nodes)
  participating in it, with averages and standard deviation shown as
  red dots. From left to right, experiments 4/4, 4/24 and 7/31.}
\label{fig:duration}
\end{figure}
%
We will have to analyze experiment data a bit further to find out why
this happens and also if there is some pattern in the three sets of
experiments. An interesting question to ask, for instance, is if
adding more computers makes the experiment take less.
